Future Directions

### 2021-02-28 manuscripts/laplacian_smoothing/AISTATS/minimax_optimal_laplacian_smoothing.tex

To summarize: for $d = 1,2,$ or $3$, with high probability, the Laplacian smoothing estimator \smash{$\wh{f}$} has in-sample mean squared error that is within a constant factor of the minimax error. Some remarks:
\begin{itemize}
  \item The first-order Sobolev space $H^1(\Xset)$ does not continuously embed into $C^0(\Xset)$ when $d>1$ (in general, the $k$th order space $H^k(\Xset)$ does not continuously embed into $C^0(\Xset)$ except if $2k>d$). For this reason, one really cannot speak of pointwise evaluation of a Sobolev function $f_0 \in H^1(\Xset)$ when $d>1$ (as we do in Theorem~\ref{thm:laplacian_smoothing_estimation1} by defining our target of estimation to be $f_0(X_i)$, $i=1,\ldots,n$). We can resolve this by appealing to what are known as \emph{Lebesgue points}, as explained in the supplement.
% RJT: Alden, please add a section to the supplement to explain this part.
% AJG: Added.
	\item The assumption $M \leq n^{1/d}$ ensures that the upper bound provided in the theorem is meaningful (i.e., ensures it is of most a constant order).
	\item The lower bound on $r$ imposed in condition \ref{asmp:ls_kernel_radius_estimation} is compatible with practice, where by far the most common choice of radius is the connectivity threshold \smash{$r \asymp (\log(n)/n)^{1/d}$}, which makes \smash{$G_{n,r}$} as sparse as possible while still being connected, for maximum computational efficiency. The upper bound may seem a bit more mysterious---we need it for technical reasons to ensure that \smash{$\wh{f}$} does not overfit, but note that as a practical matter one rarely chooses $r$ to be so large anyway.
	\item It is possible to extend \smash{$\wh{f}$} to be defined on all of $\Xset$ and then evaluate the error of such an extension (as measured against $f_0$) in $\Leb^2(\Xset)$ norm. When \smash{$\wh{f}$} and $f_0$ are suitably smooth, tools from empirical process theory (see e.g., Chapter 14 of \citet{wainwright2019}) or approximation theory (e.g., Section 15.5 of \citet{johnstone2011}) guarantee that the $\Leb^2(\Xset)$ error is not too much greater than its in-sample counterpart. In fact, as shown in the supplement, if $f_0$ is Lipschitz smooth and we extend \smash{$\wh{f}$} to be piecewise constant over the Voronoi tesselation induced by $X_1,\ldots,X_n$, then the out-of-sample error \smash{$\|\wh{f}-f_0\|_{\Leb^2(\Xset)}$} is within a negligible factor of the in-sample error \smash{$\|\wh{f}-f_0\|_n$}. We leave analysis of the Sobolev case to future work.
	\item Additionally, under the stronger assumption that $f_0$ is Lipschitz smooth, we can replace the factor of $\delta$ in the high probability bound by the sharper $\delta^2/n$.
\end{itemize}

>>>>

To summarize: for $d = 1,2,$ or $3$, with high probability, the Laplacian smoothing estimator \smash{$\wh{f}$} has in-sample mean squared error that is within a constant factor of the minimax error. Some remarks:
\begin{itemize}
  \item The first-order Sobolev space $H^1(\Xset)$ does not continuously embed into $C^0(\Xset)$ when $d>1$ (in general, the $k$th order space $H^k(\Xset)$ does not continuously embed into $C^0(\Xset)$ except if $2k>d$). For this reason, one really cannot speak of pointwise evaluation of a Sobolev function $f_0 \in H^1(\Xset)$ when $d>1$ (as we do in Theorem~\ref{thm:laplacian_smoothing_estimation1} by defining our target of estimation to be $f_0(X_i)$, $i=1,\ldots,n$). We can resolve this by appealing to what are known as \emph{Lebesgue points}, as explained in the supplement.
% RJT: Alden, please add a section to the supplement to explain this part.
% AJG: Added.
	\item The assumption $M \leq n^{1/d}$ ensures that the upper bound provided in the theorem is meaningful (i.e., ensures it is of most a constant order).
	\item The lower bound on $r$ imposed in condition \ref{asmp:ls_kernel_radius_estimation} is compatible with practice, where by far the most common choice of radius is the connectivity threshold \smash{$r \asymp (\log(n)/n)^{1/d}$}, which makes \smash{$G_{n,r}$} as sparse as possible while still being connected, for maximum computational efficiency. The upper bound may seem a bit more mysterious---we need it for technical reasons to ensure that \smash{$\wh{f}$} does not overfit, but note that as a practical matter one rarely chooses $r$ to be so large anyway.
	\item It is possible to extend \smash{$\wh{f}$} to be defined on all of $\Xset$ and then evaluate the error of such an extension (as measured against $f_0$) in $\Leb^2(\Xset)$ norm. When \smash{$\wh{f}$} and $f_0$ are suitably smooth, tools from empirical process theory (see e.g., Chapter 14 of \citet{wainwright2019}) or approximation theory (e.g., Section 15.5 of \citet{johnstone2011}) guarantee that the $\Leb^2(\Xset)$ error is not too much greater than its in-sample counterpart. In fact, as shown in the supplement, if $f_0$ is Lipschitz smooth and we extend \smash{$\wh{f}$} to be piecewise constant over the Voronoi tesselation induced by $X_1,\ldots,X_n$, then the out-of-sample error \smash{$\|\wh{f}-f_0\|_{\Leb^2(\Xset)}$} is within a negligible factor of the in-sample error \smash{$\|\wh{f}-f_0\|_n$}. We leave analysis of the Sobolev case to future work.
	\item Under the assumption that $f_0$ is Lipschitz smooth, we can also replace the factor of $\delta$ in the high probability bound by the sharper $\delta^2/n$.
\end{itemize}
